### 2024-04-04 scripts/02-data_cleaning.qmd
update

# Change from json format to csv
csv_file <- here::here("data/analysis_data/cleaned_json_data.csv")

# Write the cleaned data frame to a CSV file
write_csv(cleaned_json_data, csv_file)

>>>>

# Change from json format to csv
csv_file <- here::here("data/analysis_data/cleaned_pocket_area_data.csv")

# Write the cleaned data frame to a CSV file
write_csv(cleaned_pocket_area_data, csv_file)
